---
output: github_document
---

# Installation

```{r installation, eval=FALSE}
if (!"remotes" %in% installed.packages()) {
  install.packages("remotes")
}
remotes::install_github("thomas-neitmann/ggcharts")
```

# Usage

## Basics

Let's start off by loading some data for plotting. `ggcharts` comes with the `biomedicalrevenue` dataset which contains annual revenues (in billion USD) of top biomedical companies from 2011 to 2018.

```{r, message=FALSE}
library(dplyr)
library(ggcharts)
data("biomedicalrevenue")
head(biomedicalrevenue, 10)
```

Now that we have our data let's create a basic `bar_chart()` and `lollipop_chart()`.

```{r basics, out.width='50%', fig.show='hold'}
biomedicalrevenue %>%
  filter(year == 2017) %>%
  bar_chart(company, revenue)

biomedicalrevenue %>%
  filter(year == 2018) %>%
  lollipop_chart(company, revenue)
```

From this little example you can already see some important features of `ggcharts`:

- the data is sorted prior to plotting without you having to take care of that; if that is not desireable set `sort = FALSE`
- the plot is horizontal by default; this can be changed by setting `horizontal = FALSE`
- `ggcharts` uses `theme_minimal()`

## Using the limit argument

The plots above contain data from all companies. What if you want to display only the top 10? That's easy, just set `limit = 10`.

```{r limit, out.width='50%', fig.show='hold'}
biomedicalrevenue %>%
  filter(year == 2017) %>%
  bar_chart(company, revenue, limit = 10)

biomedicalrevenue %>%
  filter(year == 2018) %>%
  lollipop_chart(company, revenue, limit = 10)
```

## Changing colors

```{r colors, out.width='50%', fig.show='hold'}
biomedicalrevenue %>%
  filter(year == 2017) %>%
  bar_chart(company, revenue, bar_color = "#b32134", limit = 10)

biomedicalrevenue %>%
  filter(year == 2018) %>%
  lollipop_chart(
    company, revenue, 
    point_color = "darkgreen", line_color = "gray", 
    limit = 10
  )
```

## Facetting

```{r facet, message=FALSE}
biomedicalrevenue %>%
  filter(year %in% c(2011, 2018)) %>%
  bar_chart(company, revenue, year, limit = 5)
```
