---
output: github_document
title: "ggcharts"
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  fig.path = "man/figures/README-"
)
```


[![Build Status](https://travis-ci.com/thomas-neitmann/ggcharts.svg?branch=master)](https://travis-ci.com/thomas-neitmann/ggcharts)
[![CRAN Version](https://www.r-pkg.org/badges/version/ggcharts?color=green)](https://cran.r-project.org/package=ggcharts)
[![Total Downloads](http://cranlogs.r-pkg.org/badges/grand-total/ggcharts?color=green)](https://cran.r-project.org/package=ggcharts)
[![Lifecycle Status](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)

## Overview

`ggcharts` provides a high-level `ggplot2` interface for creating common charts. Its aim is both simple and ambitious: shorten the distance from data visualization idea to actual plot. How so? By taking care of a lot of data preprocessing, obscure `ggplot2` details and plot styling for you. The resulting plots are `ggplot` objects and can be further customized using any `ggplot2` function.

## Installation

The package is available from CRAN.

```{r install_cran, eval=FALSE}
install.packages("ggcharts")
```

Alternatively, you can install the latest development version from GitHub.

```{r install_github, eval=FALSE}
if (!"remotes" %in% installed.packages()) {
  install.packages("remotes")
}
remotes::install_github("thomas-neitmann/ggcharts", upgrade = "never")
```

## Why ggcharts?

Thanks to `ggplot2` you can create beautiful plots in `R`. However, it can often take quite a bit of effort to get from a data visualization idea to an actual plot. As an example, let's say you want to create a faceted bar chart displaying the top 10 within each facet ordered from highest to lowest. What sounds simple is actually pretty hard to achieve. Have a look:

```{r motivation, message=FALSE, warning=FALSE}
library(dplyr)
library(ggplot2)
library(ggcharts)
data("biomedicalrevenue")

biomedicalrevenue %>%
  group_by(year) %>%
  top_n(10, revenue) %>%
  ungroup() %>%
  mutate(company = tidytext::reorder_within(company, revenue, year)) %>%
  ggplot(aes(company, revenue)) +
  geom_col() +
  coord_flip() +
  tidytext::scale_x_reordered() +
  facet_wrap(vars(year), scales = "free_y")
```

That's a lot of code! And you likely never heard of some of the functions involved. With ggcharts you can create the same plot (actually an even better looking one) in a single line of code.

```{r motivation_continued}
bar_chart(biomedicalrevenue, company, revenue, facet = year, limit = 10)
```

That's the beauty of `ggcharts`: shortening the distance between data visualization idea and actual plot as much as possible.

## Features

Currently `ggcharts` includes the following functions:

- `bar_chart()`
- `diverging_bar_chart()`
- `column_chart()`
- `lollipop_chart()`
- `diverging_lollipop_chart()`
- `dumbbell_chart()`

You can learn more about these functions [here](https://thomas-neitmann.github.io/ggcharts/reference/index.html).
