---
title: "Make Your Plots Stand Out with Highlights"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{highlight}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Introduction

```{r, include = FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  warning = FALSE,
  fig.width = 5.5,
  fig.height = 5.5
)
```

The `ggcharts` package currently offers two functions with a `highlight` parameter: `bar_chart()` and `lollipop_chart()`. The usage is the same for both functions.

```{r setup, message=FALSE, warning=FALSE}
library(ggcharts)
library(dplyr)
data("biomedicalrevenue")
revenue2018 <- biomedicalrevenue %>%
  filter(year == 2018)
```


## Basic Usage

In its most simple form the `highlight` feature can be used to highlight a single bar or lollipop. 

```{r, warning=FALSE}
bar_chart(
  revenue2018,
  company,
  revenue,
  top_n = 10,
  highlight = "Roche"
)
```

The color for the highlighted and non-highlighted values are automatically determined from the currenty active `ggcharts` theme, i.e. `ggcharts_get_theme()`. Thus, changing the theme will change these colors.

```{r}
ggcharts_set_theme("theme_ng")
bar_chart(
  revenue2018,
  company,
  revenue,
  top_n = 10,
  highlight = "Roche"
)
```


## Changing the (Non-)Highlight Color

To set the highlight and non-highlight colors manually you will need to pass a `highlight_spec()` to the `highlight` argument.

```{r}
ggcharts_set_theme("theme_ggcharts")
spec <- highlight_spec(
  what = "Roche",
  highlight_color = "black",
  other_color = "lightgray"
)
bar_chart(
  revenue2018,
  company,
  revenue,
  top_n = 10,
  highlight = spec
)
```


## Highlighting Multiple Data Points

To highlight more than one value pass a vector to `highlight`.

```{r}
bar_chart(
  revenue2018,
  company,
  revenue,
  top_n = 10,
  highlight = c("Roche", "Novartis")
)
```

To highlight multiple values in different colors you will need to use a `highlight_spec()` again.

```{r}
spec <- highlight_spec(
  what = c("Roche", "Novartis"),
  highlight_color = c("steelblue", "darkorange")
)
lollipop_chart(
  revenue2018,
  company,
  revenue,
  top_n = 10,
  highlight = spec
)
```


## Highlight + Facet

The highlight feature is particularly useful when used in conjunction with the `facet` feature.

```{r, fig.width=8, fig.height=8}
biomedicalrevenue %>%
  filter(year %in% c(2012, 2014, 2016, 2018)) %>%
  bar_chart(
    company,
    revenue,
    facet = year,
    top_n = 12,
    highlight = "Bayer"
  )
```

