---
title: "Make Your Plots Stand Out with Highlights"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{highlight}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Introduction

```{r, include = FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  warning = FALSE,
  fig.width = 5.5,
  fig.height = 5.5
)
```

The `ggcharts` package currently offers two functions with a `highlight` parameter: `bar_chart()` and `lollipop_chart()`. Unless otherwise noted the usage is the same for both functions.

```{r setup, message=FALSE, warning=FALSE}
library(ggcharts)
library(dplyr)
data("biomedicalrevenue")
revenue2018 <- biomedicalrevenue %>%
  filter(year == 2018)
```


## Basic Usage

In its most simple form the `highlight` feature can be used to highlight a single bar or lollipop.

```{r, warning=FALSE}
bar_chart(
  revenue2018,
  company,
  revenue,
  limit = 10,
  highlight = "Roche"
)
```


## Changing the Highlight Color

Changing the `highlight` color is simple: just provide a color to the `bar_color` parameter.

```{r}
bar_chart(
  revenue2018,
  company,
  revenue,
  limit = 10,
  highlight = "Roche",
  bar_color = "darkorange"
)
```

To change the `highlight` color in `lollipop_chart()` pass a color to `line_color`. Note that having a different color for the lollipop head and stick is not possible when passing a value to `highlight`. The `point_color` will simply be ignored.

```{r}
lollipop_chart(
  revenue2018,
  company,
  revenue,
  limit = 10,
  highlight = "Roche",
  line_color = "darkgreen"
)
```


## Highlighting Multiple Data Points

To highlight more than one bar pass a vector to `highlight`. Note the message that gets printed.

```{r}
bar_chart(
  revenue2018,
  company,
  revenue,
  limit = 10,
  highlight = c("Roche", "Novartis")
)
```

To highlight multiple bars in different colors pass a vector of colors to `bar_color` or `line_color` for `bar_chart()` and `lollipop_chart()`, respectively.

```{r}
lollipop_chart(
  revenue2018,
  company,
  revenue,
  limit = 10,
  highlight = c("Roche", "Novartis"),
  line_color = c("steelblue", "darkorange")
)
```


## Highlight + Facet

The highlight feature is particularly useful when used in conjunction with the `facet` feature.

```{r, fig.width=8, fig.height=8}
biomedicalrevenue %>%
  filter(year %in% c(2012, 2014, 2016, 2018)) %>%
  bar_chart(
    company,
    revenue,
    facet = year,
    limit = 12,
    highlight = "Bayer",
    bar_color = "darkgreen"
  )
```

