---
title: "Themes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{themes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Introduction

```{r, include = FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  message = FALSE,
  warning = FALSE,
  fig.width = 6,
  fig.height = 4
)
```

```{r setup}
library(ggcharts)
library(dplyr)
```

`ggcharts` offers a couple of highly customizable `ggplot2` themes. When you don't specify any arguments all themes are very minimal. They don't have any axis lines, axis ticks and grid lines. This is intentional. Depending on the chart you create different combinations of these parameters work best. You should carefully choose them on your own rather than using some arbitrary default. Let's illustrate this with `theme_hermit()`.


## Usage

### With ggplot2

```{r}
scatter <- ggplot(mtcars, aes(hp, mpg)) + geom_point(color = "darkorange")
scatter + theme_hermit()
```

As promised, this is very minimal. If you like that look feel free to leave it like this otherwise customize it for your needs. For this scatter plot you might choose to have axis lines and ticks. This can easily be achieved.

```{r}
scatter + theme_hermit(axis = "xy", ticks = "xy")
```

Alternatively, you may want to use grid lines.

```{r}
scatter + theme_hermit(grid = "XY")
```

Notice that I used uppercase `"XY"` which will draw major grid lines. For minor grid lines use lowercase `"xy"` and for a combination use `"XYxy"`.

Next, let's have a look at a histogram example.

```{r message=FALSE, warning=FALSE}
hist <- ggplot(diamonds, aes(price)) +
  geom_histogram(fill = "darkorange", color = "white") +
  scale_y_continuous(expand = expand_scale(mult = c(0, .05)))
hist + theme_nightblue()
```

For this chart the minimal default doesn't look too bad but you might want to add horizontal grid lines.

```{r}
hist + theme_nightblue(grid = "X")
```

Additionally you may want to add an x axis line and ticks.

```{r}
hist + theme_nightblue(grid = "X", axis = "x", ticks = "x")
```


### With ggcharts

`ggcharts` uses `theme_ggcharts()` by default and sets the `axis`, `tick` and `grid` arguments automatically depending on the plot. You can change the theme by using `ggcharts_set_theme()`.

```{r}
lollipop_chart(diamonds, cut, highlight = "Good")
ggcharts_set_theme("theme_ng")
lollipop_chart(diamonds, cut, highlight = "Good")
```

The advantage of using `ggcharts_set_theme()` over adding the theme to a `ggcharts` plot is two-fold. First, as already mentioned the theme arguments are set automatically. Second, the default color used for the geom is changed. Finally, the color of the non-highlighted bars/lollipops is determined automatically from the theme background.


## Gallery

### `theme_ggcharts`

This is the default theme of `ggcharts`.

```{r}
scatter + theme_ggcharts(axis = "xy")
```

```{r}
hist + theme_ggcharts(axis = "x", grid = "X")
```


### `theme_ng`

```{r}
scatter + theme_ng(grid = "XYxy")
```


```{r}
hist + theme_ng(axis = "xy", ticks = "y")
```


### `theme_hermit`

```{r}
spec <- highlight_spec("Roche", "yellow", "#7A7A7A")
biomedicalrevenue %>%
  filter(year %in% c(2011, 2013, 2015, 2017)) %>%
  lollipop_chart(company, revenue, facet = year, highlight = spec, top_n = 5) +
  theme_hermit(axis = "y", grid = "Y")
```


### `theme_nightblue`

```{r}
biomedicalrevenue %>%
  filter(company == "Novartis") %>%
  ggplot(aes(year, revenue)) +
  geom_line(color = "darkorange", size = 1) +
  theme_nightblue(axis = "x", ticks = "x", grid = "XY")
```

```{r cleanup, include=FALSE}
ggcharts_set_theme("theme_ggcharts")
```
